---
title: "Exploring Objectives with `R`-Optimization Infrastructure (`ROI`)"
author: Vinit Kaushik
output: github_document
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r Setup, message=F, include=FALSE}
# date: !r Sys.Date()
knitr::opts_chunk$set(cache = TRUE, cache.path='cache/')
# knitr::opts_chunk$set(fig.width=12, fig.height=8)
```

We shall adapt various vignettes for this research viewpoint, while building further on what's discussed at earlier viewpoint [Risk-free Nay Ratna]. That way, we raise workability and avoid inadvertent programming errors. From each heading's hyperlink, readers can also refer to the vignette for the corresponding heading's text to aid understanding. As a vignette says, this is to "solve complex optimization problems." The reader might find this viewpoint technically challenging, but wading through this will help the reader prefer a smaller set of Objectives to refine further (e.g., using custom Moments) and test them in out-of-sample settings using re-balancing, before possibly considering investing using them. The [author](mailto:yadevinit@gmail.com) recommends that the reader at least browse through the content under heading [6.4 Maximize quadratic utility with ROI]; that seems to call for further support using a coherent risk measure `ES`, maybe superior Moment estimates, and out-of-sample test via re-balancing.

# A. [Custom Moment and Objective Functions 2018-May] Adapted

## 1 Getting Started: Load Packages and Data

```{r dataPrepR, echo=FALSE}
CaGRtoCwGR <- function(CaGR, aByw=52/1){
  CwGR <- -1 + exp((1/aByw) * log(1+CaGR))
  return(CwGR)
}
myCountNA0omits <- function(myCol){
  exna0 <- na.omit(myCol)
  exna0 <- exna0[which(exna0 != 0.0)] # coz 0.0 log return is likely to be missing data.
  return(length(exna0))
}
colTail1.asset <- function(assetName, yNonNA0, yNonNA0.which){
  ixVec <- yNonNA0[yNonNA0.which[, assetName], assetName]
  if(length(ixVec) > 0){
    asseTail <- tail(ixVec, 1)
  } else {
    gNamesNA0 <<- c(gNamesNA0, assetName)
    asseTail <- NA # Note: tail(c()) == NULL
  }
  return(as.numeric(asseTail))
}
colTail1 <- function(yNonNA0, yNonNA0.which){
  ans <- do.call(c, lapply(colnames(yNonNA0), FUN=colTail1.asset, yNonNA0, yNonNA0.which))
  return(ans)
}
getLastNonNA0 <- function(i, y, cLookBackRows=(7-1)){
  # ref https://stackoverflow.com/questions/9992421/constant-size-period-apply-with-irregularly-spaced-endpoints-in-r
  stopifnot(i > cLookBackRows)
  yNonNA0 <- y[(i - cLookBackRows) : i,]
  yNonNA0.which <- !(is.na(yNonNA0) | yNonNA0 == 0) # Beware: not scalar || `or`.
  tmp.d3 <- colTail1(yNonNA0, yNonNA0.which)
  #yNonNA0.which.exists <- all(yNonNA0.which) # Beware: single-value (as vector) returned by any().
  #stopifnot(all(yNonNA0.which.exists))
  #yNonNA0 <- yNonNA0[yNonNA0.which,]
  ytail <- xts(t(tmp.d3), index(y)[i]) # Without t(), error:
    # [Error in xts(tmp.d3, index(y)[i]) : NROW(x) must match length(order.by)].
  colnames(ytail) <- colnames(y)
  return(ytail)
}
myAssetsWithReturnsOverCompletePeriod <- function(argIsLogReturns=TRUE, argix,
  dateRange=cDateRange, myPeriod="weeks", minProp=1.0){
  require(xts)
  x <- argix[dateRange,]; print(periodicity(x)); print(dim(x))
  ep <- endpoints(x, on=myPeriod, k=1) # k=number of sub periods to aggregate on
  if(argIsLogReturns){
    print("Argument given to be summable (daily) log returns.")
    paout <- period.apply(x, INDEX=ep, FUN=colSums, na.rm=TRUE)
    countNA0omits <- apply(paout, 2, myCountNA0omits)
    # countNonNA <- colSums(!is.na(df)) # count non NAs
    mustDropCols <- ((countNA0omits / (length(ep) - 1)) < minProp) # coz ep includes 0 at start.
    ans <- paout[, mustDropCols] # subset(paout, select=-mustDropCols)
  } else {
    # Use lapply to call your function at each endpoint (removing first endpoint which == zero) 
    # do.call(rbind, lapply(endpoints(x, 'months')[-1], FUN=getLastNonNA0, y=x))
    gNamesNA0 <<- c()
    tmp2.ep <- endpoints(x, on="weeks", k=1)[-1] # coz 0,2,9,... can happen!
    tmp2.tail1 <- getLastNonNA0(i=tmp2.ep[2], y=x, cLookBackRows=(tmp2.ep[2]-tmp2.ep[1] -1))
    x <- x[, setdiff(colnames(x), unique(gNamesNA0))] # Drop columns that miss data.
    gNamesNA0.bak <<- gNamesNA0; gNamesNA0 <<- c()
    lastNonNA0 <- do.call(rbind, lapply(tail(tmp2.ep, -1), FUN=getLastNonNA0, y=x))
    stopifnot(length(gNamesNA0) == 0) # Assert there are no more dropped names.
    ans <- xts::diff.xts(lastNonNA0, lag=1, differences=1, log=TRUE) # , arithmetic=TRUE
    ans <- ans[-1,] # Drop row 1 which has NAs.
  }
  print(dim(ans))
  return(ans)
}
flagExtremes <- function(assetName, argix, absLim=0.30){
  argixVec <- argix[, assetName]
  mustFlag <- which(abs(argixVec) >= absLim)
  if(length(mustFlag) > 0){
    ans <- argixVec[mustFlag]
  } else {
    ans <- NA
  }
  return(ans)
}
```

```{r GettingStarted}
library(ROI)
library(ROI.plugin.glpk)
library(ROI.plugin.quadprog)
# library(DEoptim)
library(PortfolioAnalytics)

date()
matchVignette <- FALSE # TRUE iff vignette data (including dates) and outputs are to be matched
quRiskAversion <- c(0.25, 2, 10, 25)[ifelse(matchVignette, 1, 2)]
  # Alt: 10 which shows up in Example 4. 25 is within 20-30 range mentioned in CMU paper.
if(matchVignette){
  data(edhec)
    # Use the first 4 columns in edhec for a returns object
  cDateRange <- '::2014-01-31' # Was '::2018-05-17' coz specified vignette's date is 2018-May-17
  R <- edhec[cDateRange, 1:4] # Subset to match cDateRange, instead of tail() with 2019 data too.
  colnames(R) <- c("CA", "CTAG", "DS", "EM")
} else {
  cMyPath <- "F:/pf4pf/data/indices/"; warning("cannot include others' data into repos")
  cFileIndex <- "assets-"
  gIx <- readRDS(file=paste0(cMyPath, cFileIndex, ".rds"))
  cDateRange <- c("2001/", # gets earliest large slice of assets.
    "2007/", # gets at least a window of a year to train/learn on before entering 2008 GFC.
      # "2004/" includes GLD and GOLDBEES. Early "2006" includes SLV too.
    "2010-07/" # TSLA data starts.
  )[3]; cDateRange <- paste0(cDateRange, "2020-11")
  argIsLogReturns <- FALSE
  if(! argIsLogReturns){
    R <- equity.data <- myAssetsWithReturnsOverCompletePeriod(argIsLogReturns, argix=gIx,
      dateRange=cDateRange, myPeriod="weeks", minProp=1.0)
  } else {
    R <- equity.data <- myAssetsWithReturnsOverCompletePeriod(argIsLogReturns, argix=gIxLogR,
      dateRange=cDateRange, myPeriod="weeks", minProp=1.0)
  }
}
str(R)
head(R, 2)
tail(R, 2)
# Get a character vector of the fund names
funds <- colnames(R)
```

## 2 Setting the Portfolio Moments
```{r SettingMoments}
library(PortfolioAnalytics)
# Construct initial portfolio with basic constraints.
init.portFL <- portfolio.spec(assets=funds)
init.portFL <- add.constraint(portfolio=init.portFL, type="full_investment")
init.portFL <- add.constraint(portfolio=init.portFL, type="long_only")
# Portfolio with standard deviation as an objective
SD.portf <- add.objective(portfolio=init.portFL, type="risk", name="StdDev")
# Portfolio with expected shortfall as an objective
ES.portf <- add.objective(portfolio=init.portFL, type="risk", name="ES")
sd.moments <- set.portfolio.moments(R, SD.portf)
names(sd.moments)
es.moments <- set.portfolio.moments(R, ES.portf)
names(es.moments)
```

## 3 Custom Moment Functions
```{r CustomMoment}
sigma.robust <- function(R){
  require(MASS)
  out <- list()
  set.seed(1234)
  out$sigma <- cov.rob(R, method="mcd")$cov
    # Ref https://r.789695.n4.nabble.com/Using-optimize-portfolio-td4763805.html:
    # sigma <- cov(returns) # but then I changed it to
    # sigma <- cov(returns, use = "pairwise.complete.obs") # per Brian's suggestion
  return(out)
}
opt.sd <- optimize.portfolio(R, SD.portf,
  optimize_method="ROI",
  momentFUN="sigma.robust")
opt.sd
  # Beware: possibly due to data range, this output differs
  # from that of vignette (though the Objective StdDev is close) which says:
  # Optimal Weights:
  # CA CTAG DS EM
  # 0.6598 0.1441 0.1961 0.0000
  # Objective Measure:
  # StdDev
  # 0.008646
  # but StdDev verifies sqrt() == extractObjectiveMeasures()$StdDev.
  # So, robust estimate of the covariance matrix was indeed used.
weights <- extractWeights(opt.sd)
sigma <- sigma.robust(R)$sigma
sqrt(t(weights) %*% sigma %*% weights)
extractObjectiveMeasures(opt.sd)$StdDev
chart.Weights(opt.sd)
```


# B. [Introduction to PortfolioAnalytics 2018-May] Adapted

## 6.1 Initial Portfolio Object
```{r initPortfolio, echo=TRUE}
if(matchVignette){
  data(edhec)
  R <- edhec[cDateRange, 1:6]
  colnames(R) <- c("CA", "CTAG", "DS", "EM", "EQMN", "ED")
  dim(R)
  head(R, 2); tail(R, 2)
  funds <- colnames(R)
  # Create an initial portfolio object with leverage and box constraints
  init <- portfolio.spec(assets=funds)
  init <- add.constraint(portfolio=init, type="leverage",
    min_sum=0.99, max_sum=1.01)
  init <- add.constraint(portfolio=init, type="box", min=0.05, max=0.65)
} else {
  init <- init.portFL # portf0LI
}
```

## 6.2 Maximize mean return with ROI
```{r maxMeanROI}
maxret <- add.objective(portfolio=init, type="return", name="mean")
print(maxret)
# Run the optimization.
opt_maxret <- optimize.portfolio(R=R, portfolio=maxret, optimize_method="ROI", trace=TRUE)
print(opt_maxret)
plot(opt_maxret, risk.col="StdDev", return.col="mean",
  main="Maximum Return Optimization", chart.assets=TRUE)
  # , xlim=c(0, 0.05), ylim=c(0,0.0085)
# extractStats(opt_maxret)
chart.Weights(opt_maxret)
```
That does maximize (mean) return, but if the investor is unwilling to tolerate the associated risk (or in this case, volatility in the form of `StdDev`) and such a concentrated portfolio, we need to explore further.

## 6.4 Maximize quadratic utility with ROI
You might recall earlier research viewpoint [Nay Ratna] sharing a commitment to transform the wealth ecosystem onto another realm of growth with harmonized incentive structures, e.g., a business model with fees based on Net Present Value. That seems to be consistent with an investor-customizable risk aversion, as part of a (CRRA-maximization or other) portfolio objective. And the harmonization vibes with ["Skin in the Game: Hidden Asymmetries in Daily Life"]:

> If an actor pockets some rewards from a policy they enact or support without accepting any of the risks, economists consider it to be a problem of "missing incentives". In contrast, to Taleb, the problem is more fundamentally one of asymmetry: one actor gets the rewards, the other is stuck with the risks.[1]
Taleb argues that "For social justice, focus on symmetry and risk sharing. You cannot make profits and transfer the risks to others, as bankers and large corporations do ... Forcing skin in the game corrects this asymmetry better than thousands of laws and regulations."

```{r maxQuadUtilityROI}
qu <- add.objective(portfolio=init, type="return", name="mean")
qu <- add.objective(portfolio=qu, type="risk", name="var", risk_aversion=quRiskAversion)
# Run the optimization.
opt_qu <- optimize.portfolio(R=R, portfolio=qu, optimize_method="ROI", trace=TRUE)
print(opt_qu)
  # Output differs from vignette's, especially weights for DS and EM assets and objectives
  # mean and StdDev:
  # Optimal Weights:
  # CA CTAG DS EM EQMN ED
  # 0.0500 0.0500 0.2714 0.5386 0.0500 0.0500
  # Objective Measure:
  # mean
  # 0.007926
  # StdDev
  # 0.02663
plot(opt_qu, risk.col="StdDev", return.col="mean",
  main=paste0("Risk Aversion=", quRiskAversion, " Quadratic Utility Optimization"),
  chart.assets=TRUE) # , xlim=c(0, 0.05), ylim=c(0, 0.0085)
chart.Weights(opt_qu)
```

## 6.5 Minimize expected tail loss with ROI
If the exploration so far is making the investor loss averse, let's take this position now, with a coherent measure of risk `ETL` (also known as `CVaR` or `ES`) instead of `StdDev`.
```{r minETLwithROI}
etl <- add.objective(portfolio=init, type="risk", name="ETL")
# Run the optimization.
opt_etl <- optimize.portfolio(R=R, portfolio=etl, optimize_method="ROI", trace=TRUE)
print(opt_etl)
# Differs from vignette's CTAG and EQMN weights as well as objective ETL:
# Optimal Weights:
# CA CTAG DS EM EQMN ED
# 0.0500 0.2968 0.0500 0.0500 0.4932 0.0500
# Objective Measure:
# ETL
# 0.01967
plot(opt_etl, risk.col="ES", return.col="mean", main="ETL Optimization", chart.assets=TRUE)
  # , xlim=c(0, 0.14), ylim=c(0,0.0085)
chart.Weights(opt_etl)
```


# C. [Maximizing Modified Sharpe Ratio Demo 2014] Adapted
This gets you what's called as a tangency portfolio.
```{r maxModifiedSharpeSTARR}
#' This script demonstrates how to solve a constrained portfolio optimization 
#' problem to maximize modified Sharpe Ratio using ES as the risk measure.
# full_investment and long_only without relaxed weights are preferred.
init.portf <- add.objective(portfolio=init.portFL, type="return", name="mean")
init.portf <- add.objective(portfolio=init.portf, type="risk", name="ES",
                            arguments=list(p=0.925))
init.portf

#' Maximizing STARR Ratio can be formulated as a linear programming 
#' problem and solved very quickly using optimize_method="ROI". 
#' The default action if "mean" and "ES" are specified as objectives with
#' optimize_method="ROI" is to maximize STARR. If we want to use
#' both mean and ES in the objective function, but only minimize ES, we need to 
#' pass in maxSTARR=FALSE to optimize.portfolio.
maxSTARR.lo.ROI <- optimize.portfolio(R=R, portfolio=init.portf, optimize_method="ROI",
  trace=TRUE) # maxSTARR=TRUE default for mean-ES
maxSTARR.lo.ROI
chart.RiskReward(maxSTARR.lo.ROI, risk.col="ES", return.col="mean", chart.assets=TRUE)
chart.Weights(maxSTARR.lo.ROI)
# Calculate STARR ratio from efficient frontier and optimization; they are identical:
ef2 <- create.EfficientFrontier(R=R, portfolio=init.portf, type="mean-ES", n.portfolios=100)
max(ef2$frontier[,"mean"] / ef2$frontier[,"ES"])
maxSTARR.lo.ROI$objective_measures$mean / maxSTARR.lo.ROI$objective_measures$ES
chart.EfficientFrontier(ef2)
```

## Appendix
Here's the runtime environment used. It's reported here for reproducibility:
```{r Closing}
Sys.info()[['sysname']]
sessionInfo()
```

[Risk-free Nay Ratna]: <https://github.com/yadevinit/pf4pf/blob/main/riskfreeNayRatna.md>
[Custom Moment and Objective Functions 2018-May]: <https://cran.r-project.org/web/packages/PortfolioAnalytics/vignettes/custom_moments_objectives.pdf>
[Introduction to PortfolioAnalytics 2018-May]: <https://cran.r-project.org/web/packages/PortfolioAnalytics/vignettes/portfolio_vignette.pdf>
[Complex Portfolio Optimization with PortfolioAnalytics R/Finance 2014 Ross Bennett]: <https://rossb34.github.io/PortfolioAnalyticsPresentation/>
[Advanced Moment Estimation & Optimization with PortfolioAnalytics 2015]: <http://past.rinfinance.com/agenda/2015/workshop/RossBennett.pdf>
["Skin in the Game: Hidden Asymmetries in Daily Life"]: <https://en.wikipedia.org/wiki/Skin_in_the_Game_(book)>
[Nay Ratna]: <https://github.com/yadevinit/pf4pf/blob/main/nayRatna/nayRatna.md>
[Maximizing Modified Sharpe Ratio Demo 2014]: <https://github.com/braverock/PortfolioAnalytics/blob/master/demo/demo_max_STARR.R>
[R Optimization Infrastructure (`ROI`)]: <https://cran.r-project.org/package=ROI>
