---
title: "Nay Ratna"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Background
In early 2020-Nov, this [author](mailto:yadevinit@gmail.com) messaged his former schoolmates: "Struggling with Portfolio Optimization with an objective of maximizing Net Present Value. Didn't realize optimization was such a hard problem: maximizing (mean) return while also minimizing risk (Extreme Shortfall)". Some friends joked on the understandability. A friend asked if the author was into shares trading and messaged: "I have some. But down by 65%. Bought 6 years back. Sort of stuck. Not getting any positive solutions to mitigate the losses."
